Metrics

### 2024-04-15 src/plots.Rmd
Fix dim for gen agerange perf plots

    # Save the plot
    print(ar2plot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange2-%s.pdf", a),
        plot = ar2plot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
    )
}
```

>>>>

    # Save the plot
    print(ar2plot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange2-%s.pdf", a),
        plot = ar2plot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 3 else if (a == "neo") 2.5 else NA
    )
}
```
